Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-08-26 Supplemental-Material-A-Annotated-Analysis.Rmd
Update Supplemental-Material-A-Annotated-Analysis.Rmd

To be done once initial tests approved.

@@

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS2 <- 
  dtS2Red %>% 
  select(TID, any_of(varNamS2MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  as.data.frame %>%
  mutate(date = as.character(date)) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  select_if(function(x) is.character(x) | (is.numeric(x) && sd(x) > 0)) %>%
         #which(sapply(. %>% select(where(is.numeric)), sd, na.rm = TRUE) > 0)) %>% # only vars that sd != 0
         #) %>% # only include variables that vary (i.e., sd != 0)
         #which(sd(., na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame

@@

# # Variables removed for study 2 due to high multicollinearity:
# varNamS1Out <- dtMiS1 %>%
#   select(
#     any_of(varNamDifS1),
#     mdmq.calmness.pre_calc,
#     mdmq.alertness.pre_calc,
#     mdmq.valence.pre_calc,
#     relatednessFrust.pre_calc,
#     competenceFrust.pre_calc,
#     competenceSat.pre_calc,
#     relatednessSat.pre_calc,
#     DutchFriends.pre,
#     secNatDum.pre,
#     timeNL.pre,
#     stress.post,
#     discrimination_month.post,
#     rosenberg.post,
#     qualityStar,
#     starts_with("SSAS")
#   ) %>%
#   names

# dtMiS2Fin <- dtMiS2 %>%
#   # mutate(
#   #   assimilation.dif = assimilation.post - assimilation.pre,
#   #   integration.dif = integration.post - integration.pre,
#   #   marginalization.dif = marginalization.post - marginalization.pre,
#   #   separation.dif = separation.post - separation.pre,
#   #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
#   #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
#   #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
#   #   swl.dif = swl.post_calc - swl.pre_calc
#   # ) %>% 
#   # select(
#   #   -any_of(varNamS2Out)
#   # ) %>%
#   select(PID,
#          TID,
#          TIDnum,
#          date,
#          week,
#          which(sapply(., sd, na.rm = TRUE) > 0)) %>% 
#   mutate_all(~ifelse(is.nan(.), NA, .)) %>%
#   as.data.frame

# lares::corr_cross(
#   dtMiS2 %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
```

```{r MiS2}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS2 <-
#   amelia(
#     dtMiS2,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS2, file = "data/imputed/S2Imputed.RData")
#load("data/imputed/S2Imputed.RData")

# # Imputation Stability:
# set.seed(123)
# MiS2Stability <-
#   amelia(
#     dtMiS2,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS2Stability, file = "data/imputed/S2ImputedStability.RData")
#load("data/imputed/S2ImputedStability.RData")
```

@@

To be done once initial tests approved.

```{r MiS3}
# BASED ON MiS1
```

>>>>

@@

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS2 <- 
  dtS2Red %>% 
  select(TID, any_of(varNamS2MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  as.data.frame %>%
  mutate(date = as.character(date)) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  select_if(function(x) is.character(x) | is.factor(x) | (is.numeric(x) && sd(x, na.rm = TRUE) > 0)) %>%
  as.data.frame

@@

# # Variables removed for study 2 due to high multicollinearity:
varNamS2Out <- dtMiS2 %>%
  select(
    any_of(varNamDifS2),
    ContactDesire,
    DesireIntergroup,
    DesireIngroup,
    Reason.pre,
    # mdmq.calmness.pre_calc,
    # mdmq.alertness.pre_calc,
    # mdmq.valence.pre_calc,
    # relatednessFrust.pre_calc,
    # competenceFrust.pre_calc,
    # competenceSat.pre_calc,
    # relatednessSat.pre_calc,
    # DutchFriends.pre,
    # secNatDum.pre,
    timeNL.pre,
    starts_with("HS"),
    starts_with("Home")
    # stress.post,
    # discrimination_month.post,
    # rosenberg.post,
    # qualityStar,
    # starts_with("SSAS")
  ) %>%
  names

dtMiS2Fin <- dtMiS2 %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>%
  select(
    -any_of(varNamS2Out)
  ) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
         #which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

# lares::corr_cross(
#   dtMiS2Fin %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
```

```{r MiS2}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS2 <-
#   amelia(
#     dtMiS2Fin,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS2, file = "data/imputed/S2Imputed.RData")
#load("data/imputed/S2Imputed.RData")

# # Imputation Stability:
# set.seed(123)
# MiS2Stability <-
#   amelia(
#     dtMiS2,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS2Stability, file = "data/imputed/S2ImputedStability.RData")
#load("data/imputed/S2ImputedStability.RData")
```

@@

```{r MiS3Prep}
#################################################################
##                    Variable Name Vectors                    ##
#################################################################
varNamS3MiPsbl <- c(
  paste(varNamS3MI, rep(".pre", length(varNamS3MI)), sep = ""),
  varNamS3MI,
  paste(varNamS3MI, rep(".post", length(varNamS3MI)), sep = "")
)

varNamdtS3Noms <- varNames %>%
  filter(
    aux == 1,
    format == "nominal",
    studyS3 == "S2"
  ) %>%
  select(varNam) %>%
  pull

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS3 <- 
  dtS3Red %>% 
  select(TID, any_of(varNamS3MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  as.data.frame %>%
  mutate(date = as.character(date)) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  select_if(function(x) is.character(x) | is.factor(x) | (is.numeric(x) && sd(x, na.rm = TRUE) > 0)) %>%
  as.data.frame

varNamDifS3 <- names(dtMiS3)[gsub(".pre|.post|_calc", "", names(dtMiS3)) %>% allDuplicated]

# # Variables removed for study 2 due to high multicollinearity:
varNamS3Out <- dtMiS3 %>%
  select(
    any_of(varNamDifS3),
    # ContactDesire,
    # DesireIntergroup,
    # DesireIngroup,
    # Reason.pre,
    # mdmq.calmness.pre_calc,
    # mdmq.alertness.pre_calc,
    # mdmq.valence.pre_calc,
    # relatednessFrust.pre_calc,
    # competenceFrust.pre_calc,
    # competenceSat.pre_calc,
    # relatednessSat.pre_calc,
    # DutchFriends.pre,
    # secNatDum.pre,
    # timeNL.pre,
    # starts_with("HS"),
    # starts_with("Home")
    # stress.post,
    # discrimination_month.post,
    # rosenberg.post,
    # qualityStar,
    # starts_with("SSAS")
  ) %>%
  names

dtMiS3Fin <- dtMiS3 %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>%
  select(
    -any_of(varNamS3Out)
  ) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         everything()) %>%
  mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

lares::corr_cross(
  dtMiS3Fin %>% select_if(is.numeric), # name of dataset
  max_pvalue = 0.05, # display only significant correlations (at 5% level)
  top = 20 # display top 20 couples of variables (by correlation coefficient)
)
```

```{r MiS3}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS3 <-
#   amelia(
#     dtMiS3Fin,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS3, file = "data/imputed/S3Imputed.RData")
#load("data/imputed/S2Imputed.RData")

# Imputation Stability:
# set.seed(123)
# MiS3Stability <-
#   amelia(
#     dtMiS3Fin,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS3Stability, file = "data/imputed/S3ImputedStability.RData")
#load("data/imputed/S2ImputedStability.RData")
```
